---
title: "Getting and Cleaning Data Course Project"
author: "E. Kristian Heidenreich"
date: "April 26, 2015"
output: html_document
---

Description
===
The course project for the Coursera Getting and Cleaning Data course required 
the construction of a tidy data set using _Human Activity Recognition Using
Smartphones Dataset_ found here:
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

Code Book
===

## subject_id 
#### numeric
```
Uniquely identifies the subject who performed the activity.  
Thirty unique indivuals were monitored.  
        1..30
```

## activityId 
#### character(18)
```
Identifies the activity performed by the subject.
There are six unique activities.
        WALKING
        WALKING_UPSTAIRS
        WALKING_DOWNSTAIRS
        SITTING
        STANDING
        LAYING
```

## setType 
#### character(5)
```
Identifies the subject_id's group:
        test
        train
```

## feature
#### character(25)
Measurement taken from the smartphone:

No|feature
-|--
1|tBodyAcc_mean_X
2|tBodyAcc_mean_Y
3|tBodyAcc_mean_Z
4|tBodyAcc_std_X
5|tBodyAcc_std_Y
6|tBodyAcc_std_Z
7|tGravityAcc_mean_X
8|tGravityAcc_mean_Y
9|tGravityAcc_mean_Z
10|tGravityAcc_std_X
11|tGravityAcc_std_Y
12|tGravityAcc_std_Z
13|tBodyAccJerk_mean_X
14|tBodyAccJerk_mean_Y
15|tBodyAccJerk_mean_Z
16|tBodyAccJerk_std_X
17|tBodyAccJerk_std_Y
18|tBodyAccJerk_std_Z
19|tBodyGyro_mean_X
20|tBodyGyro_mean_Y
21|tBodyGyro_mean_Z
22|tBodyGyro_std_X
23|tBodyGyro_std_Y
24|tBodyGyro_std_Z
25|tBodyGyroJerk_mean_X
26|tBodyGyroJerk_mean_Y
27|tBodyGyroJerk_mean_Z
28|tBodyGyroJerk_std_X
29|tBodyGyroJerk_std_Y
30|tBodyGyroJerk_std_Z
31|tBodyAccMag_mean
32|tBodyAccMag_std
33|tGravityAccMag_mean
34|tGravityAccMag_std
35|tBodyAccJerkMag_mean
36|tBodyAccJerkMag_std
37|tBodyGyroMag_mean
38|tBodyGyroMag_std
39|tBodyGyroJerkMag_mean
40|tBodyGyroJerkMag_std
41|fBodyAcc_mean_X
42|fBodyAcc_mean_Y
43|fBodyAcc_mean_Z
44|fBodyAcc_std_X
45|fBodyAcc_std_Y
46|fBodyAcc_std_Z
47|fBodyAccJerk_mean_X
48|fBodyAccJerk_mean_Y
49|fBodyAccJerk_mean_Z
50|fBodyAccJerk_std_X
51|fBodyAccJerk_std_Y
52|fBodyAccJerk_std_Z
53|fBodyGyro_mean_X
54|fBodyGyro_mean_Y
55|fBodyGyro_mean_Z
56|fBodyGyro_std_X
57|fBodyGyro_std_Y
58|fBodyGyro_std_Z
59|fBodyAccMag_mean
60|fBodyAccMag_std
61|fBodyBodyAccJerkMag_mean
62|fBodyBodyAccJerkMag_std
63|fBodyBodyGyroMag_mean
64|fBodyBodyGyroMag_std
65|fBodyBodyGyroJerkMag_mean
66|fBodyBodyGyroJerkMag_std


# value
#### numeric
The mean for each feature by subject_id.

No |feature|minValue|maxValue
-|--|--|-
1|tBodyAcc_mean_X|0.22159824|0.301461020
2|tBodyAcc_mean_Y|-0.04051395|-0.001308288
3|tBodyAcc_mean_Z|-0.15251390|-0.075378469
4|tBodyAcc_std_X|-0.99606864|0.626917071
5|tBodyAcc_std_Y|-0.99024095|0.616937015
6|tBodyAcc_std_Z|-0.98765866|0.609017879
7|tGravityAcc_mean_X|-0.68004316|0.974508732
8|tGravityAcc_mean_Y|-0.47989484|0.956593814
9|tGravityAcc_mean_Z|-0.49508872|0.957873042
10|tGravityAcc_std_X|-0.99676423|-0.829554948
11|tGravityAcc_std_Y|-0.99424765|-0.643578361
12|tGravityAcc_std_Z|-0.99095725|-0.610161166
13|tBodyAccJerk_mean_X|0.04268810|0.130193044
14|tBodyAccJerk_mean_Y|-0.03868721|0.056818586
15|tBodyAccJerk_mean_Z|-0.06745839|0.038053359
16|tBodyAccJerk_std_X|-0.99460454|0.544273037
17|tBodyAccJerk_std_Y|-0.98951357|0.355306717
18|tBodyAccJerk_std_Z|-0.99328831|0.031015708
19|tBodyGyro_mean_X|-0.20577543|0.192704476
20|tBodyGyro_mean_Y|-0.20420536|0.027470756
21|tBodyGyro_mean_Z|-0.07245460|0.179102058
22|tBodyGyro_std_X|-0.99427659|0.267657219
23|tBodyGyro_std_Y|-0.99421047|0.476518714
24|tBodyGyro_std_Z|-0.98553836|0.564875818
25|tBodyGyroJerk_mean_X|-0.15721254|-0.022091627
26|tBodyGyroJerk_mean_Y|-0.07680899|-0.013202277
27|tBodyGyroJerk_mean_Z|-0.09249985|-0.006940664
28|tBodyGyroJerk_std_X|-0.99654254|0.179148650
29|tBodyGyroJerk_std_Y|-0.99708158|0.295945926
30|tBodyGyroJerk_std_Z|-0.99538079|0.193206499
31|tBodyAccMag_mean|-0.98649320|0.644604325
32|tBodyAccMag_std|-0.98646454|0.428405923
33|tGravityAccMag_mean|-0.98649320|0.644604325
34|tGravityAccMag_std|-0.98646454|0.428405923
35|tBodyAccJerkMag_mean|-0.99281472|0.434490401
36|tBodyAccJerkMag_std|-0.99464692|0.450612066
37|tBodyGyroMag_mean|-0.98074085|0.418004609
38|tBodyGyroMag_std|-0.98137268|0.299975980
39|tBodyGyroJerkMag_mean|-0.99732253|0.087581662
40|tBodyGyroJerkMag_std|-0.99766607|0.250173204
41|fBodyAcc_mean_X|-0.99524993|0.537012022
42|fBodyAcc_mean_Y|-0.98903430|0.524187687
43|fBodyAcc_mean_Z|-0.98947393|0.280735952
44|fBodyAcc_std_X|-0.99660457|0.658506543
45|fBodyAcc_std_Y|-0.99068040|0.560191344
46|fBodyAcc_std_Z|-0.98722480|0.687124164
47|fBodyAccJerk_mean_X|-0.99463080|0.474317256
48|fBodyAccJerk_mean_Y|-0.98939882|0.276716853
49|fBodyAccJerk_mean_Z|-0.99201845|0.157775692
50|fBodyAccJerk_std_X|-0.99507376|0.476803887
51|fBodyAccJerk_std_Y|-0.99046808|0.349771285
52|fBodyAccJerk_std_Z|-0.99310776|-0.006236475
53|fBodyGyro_mean_X|-0.99312261|0.474962448
54|fBodyGyro_mean_Y|-0.99402549|0.328817010
55|fBodyGyro_mean_Z|-0.98595779|0.492414380
56|fBodyGyro_std_X|-0.99465219|0.196613287
57|fBodyGyro_std_Y|-0.99435309|0.646233637
58|fBodyGyro_std_Z|-0.98672527|0.522454216
59|fBodyAccMag_mean|-0.98680065|0.586637551
60|fBodyAccMag_std|-0.98764848|0.178684581
61|fBodyBodyAccJerkMag_mean|-0.99399828|0.538404846
62|fBodyBodyAccJerkMag_std|-0.99436667|0.316346415
63|fBodyBodyGyroMag_mean|-0.98653524|0.203979765
64|fBodyBodyGyroMag_std|-0.98146884|0.236659662
65|fBodyBodyGyroJerkMag_mean|-0.99761739|0.146618569
66|fBodyBodyGyroJerkMag_std|-0.99758523|0.287834616


# Some basic counts for the data set
There were a total of 30 unique subjects in this particular study.
They were divided into two group: test and train

Group | Frequency
-|-
test | 9
train | 21
**Total** | 30

There are 66 features (measurements) obtained for 
each of the 6 activity types for all 30 subjects.
```{r}
features <- 66
activities <- 6
subjects <- 30
features * activities * subjects
```

```{r, include=FALSE}
file.rename(from="code_book.md", to="CODE_BOOK.md")
```
